DeepSphere: a graph-based spherical CNN

### 2019-09-10 main.tex
time table shrec17

\begin{table}
    \centering
    \begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & F1 & mAP & params & inference [ms] & training \\ \hline
        \cite{cohen_spherical_2018} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        \cite{esteves_learning_2017} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 2h33m \\
        DeepSphere \emph{HEALPix} & 80.65 & 68.6 & 190k & 1 & 48m\\
        DeepSphere \emph{Improved HEALPix} & ? & ? & 190k & ? & ?
    \end{tabular}
    \caption{Performance of different models for SHREC'17 task. F1-score computed with sklearn, mAP from the official script of the competition.}
    \label{tab:SHREC17_class}
\end{table}

@@

\begin{table}
	\begin{tabular}{l|c c c c}
	\multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5}
	\multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
	%Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
	\cite{jiang_spherical_2019} & 94.67 & - & - & -\\
	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10.2 & 10h14m\\
	% 328'339
	\cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
	\cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
	% unknown
	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 ms & 25h \\
	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 30 ms & 13h\\
	% 12'926'432
	\end{tabular}
	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{l|c c r r}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.98ms & 2h33m \\
        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 1.0ms & 48m\\
        DeepSphere \emph{Improved HEALPix} & 80.76 & & &
    \end{tabular}
    \caption{Performance of different models}
    \label{tab:SHREC17_class}
\end{table}

>>>>

\begin{table}
    \centering
    \begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & F1 & mAP & params & inference [ms] & training \\ \hline
        \cite{cohen_spherical_2018} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        \cite{esteves_learning_2017} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 50m \\
        DeepSphere \emph{HEALPix} & 80.65 & 68.6 & 190k & 1 & 50m\\
        DeepSphere \emph{Improved HEALPix} & ? & ? & 190k & ? & ?
    \end{tabular}
    \caption{Performance of different models for SHREC'17 task. F1-score computed with sklearn, mAP from the official script of the competition.}
    \label{tab:SHREC17_class}
\end{table}

@@

\begin{table}
	\begin{tabular}{l|c c c c}
	\multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5}
	\multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
	%Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
	\cite{jiang_spherical_2019} & 94.67 & - & - & -\\
	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h14m\\
	% 328'339
	\cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
	\cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
	% unknown
	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 & 25h \\
	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h35\\
	% 12'926'432
	\end{tabular}
	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{l|c c r r}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.9ms & 47m \\
        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 0.9ms & 46m\\
        DeepSphere \emph{Improved HEALPix} & 80.76 & & &
    \end{tabular}
    \caption{Performance of different models}
    \label{tab:SHREC17_class}
\end{table}
